The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-11-15 manuscript.Rmd
[fix #93] use rolling mean instead of b-splines
[fix #85] rephrase rare phyla numbers

Further biases exist across phyla and body size. Large-bodied and easily accessible (e.g. dried specimens like shells, corals, echinoderms) specimens are over-represented in museum collections, compared with small less accessible organisms, such as the meiofauna. Of `r n_idigbio_phyla` phyla represented in iDigBio, `r records_rare_phyla$n_rare_phyla` have <500 records, and make up `r records_rare_phyla$prop_recs_rare_phyla`% of the iDigBio records. This under-representation is also manifested at the species level, while `r records_rare_phyla$prop_spp_rare_phyla_collected`% (n = `r format(records_rare_phyla$total_spp_rare_phyla_collected, big.mark=",")` total species) of the global number of species for these `r records_rare_phyla$n_rare_phyla` phyla occur in iDigBio, this proportion rises to `r records_rare_phyla$prop_spp_common_phyla_collected`% (n = `r format(records_rare_phyla$total_spp_common_phyla_collected, big.mark=",")`) for the `r n_idigbio_phyla - records_rare_phyla$n_rare_phyla` others. Yet, these undersampled taxa, especially those of small body size, are often the most abundant, and are likely to play an important role in the detection of changes in environmental quality[@Bik2012]. Additionally, the ecological implications of changes in the structure and composition of the communities of these small-bodied organisms, on higher trophic levels and ecosystems are largely unexplored.

@@

```{r id_though_time, fig.cap='Proportion of marine invertebrate specimens collected through time identified at the species level. Trend lines are  B-splines of the 3rd degree polynomial. For all groups, we observe a decline in the proportion of specimens collected that are identified at the species level, suggesting a lack of expertise to identity precisely what is collected. (\\#fig:identification-through-time)'}
knitr::include_graphics("figures/idigbio_identification_level_through_time.pdf")
```

>>>>

Further biases exist across phyla and body size. Large-bodied and easily accessible (e.g. dried specimens like shells, corals, echinoderms) specimens are over-represented in museum collections, compared with small less accessible organisms, such as the meiofauna. Of `r n_idigbio_phyla` phyla represented in iDigBio, `r records_rare_phyla$n_rare_phyla` have <500 records. While these phyla represent
`r records_rare_phyla$prop_spp_rare_phyla_collected`% (n = `r format(records_rare_phyla$total_spp_rare_phyla_collected, big.mark=",")` total species) of the global number of species, they make up `r records_rare_phyla$prop_recs_rare_phyla`% of the iDigBio records. This proportion rises to `r records_rare_phyla$prop_spp_common_phyla_collected`% (n = `r format(records_rare_phyla$total_spp_common_phyla_collected, big.mark=",")`) for the `r n_idigbio_phyla - records_rare_phyla$n_rare_phyla` other phyla. Yet, these undersampled taxa, especially those of small body size, are often the most abundant, and are likely to play an important role in the detection of changes in environmental quality[@Bik2012]. Additionally, the ecological implications of changes in the structure and composition of the communities of these small-bodied organisms, on higher trophic levels and ecosystems are largely unexplored.

@@

```{r id_though_time, fig.cap='Proportion of marine invertebrate specimens collected through time identified at the species level. Trend lines are  smoothed rolling mean on a 3 year window. For all groups, we observe a decline in the proportion of specimens collected that are identified at the species level, suggesting a lack of expertise to identity precisely what is collected. (\\#fig:identification-through-time)'}
knitr::include_graphics("figures/idigbio_identification_level_through_time.pdf")
```
